Network Configuration Synthesis with Abstract Topologies

### 2016-11-05 paper/abstraction/paper.tex
add analysis example

\newcommand{\inferencetwo}[1]{
    \node[draw, anchor=west] at (#1 + 2, 1.25) {$e_i > 0$};
    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{I-striping}};
    \node at (#1 - 1 - .11, .6) {$e_1$};
    \node at (#1 + .11, 1.5) {$e_2$};
    \node at (#1 + 2 + .11, .6) {$e_3$};
    \node at (#1 + .11 + .8, 1.5) {$e_4$};
    \node at (#1 - 1, -.8) {L$(j,k)$};
    \node at (#1 +. 5, 2.9) {S$(min(j*k,g),1)$};
    \node at (#1 + 2, -.8) {L$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
    \node at (#1, 3.3) {};
    \draw [] (#1 + .5, 2.01) circle [radius=0.4] node {$n$};
    \draw [] (#1 - 1, 0) circle [radius=0.4] node {$m$};
    \draw [] (#1 + 2, 0) circle [radius=0.4] node {$o$};
    \draw [->] (#1 - 1, .4) -- (#1 + .5, 2 - .4);
    \draw [<-] (#1 + 2, .4) -- (#1 + .5, 2 - .4);
}

@@

The rule \infrule{I-bisec} can be thought of as a programmer assertion about the bisection between two roles. The rule applies to an edge that has been annotated with a $bisec(X)$ statement, which means that there are $X$ disjoint paths between any node in role $m$ and any node in role $n$. Annotations of this form are useful for a "one big switch" type of abstraction where part of a complex network is abstracted into a single node.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=.66\columnwidth]{figures/analysis}
  \end{center}
  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
  \label{fig:example-inference}
  \vspace{-1em}
\end{figure}

Consider again the datacenter example from \S\ref{sec:overview}. For global prefixes we used the routing policy:
%
\[ \begin{array}{c}
  \$PG \Path end(TG)
\end{array} \]
\noindent
%
Suppose now we additionally add the valleyfree constraint that traffic never has takes a path with a down-up in it. Figure~\ref{fig:example-inference} shows the abstract product graph representation for this routing policy. The inference algorith starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$
\ryan{todo}

>>>>

\newcommand{\inferencetwo}[1]{
    \node[draw, anchor=west] at (#1 + 2, 1.25) {$e_i > 0$};
    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{I-striping}};
    \node at (#1 - 1 - .11, .6) {$e_1$};
    \node at (#1 + .11, 1.5) {$e_2$};
    \node at (#1 + 2 + .11, .6) {$e_3$};
    \node at (#1 + .11 + .8, 1.5) {$e_4$};
    \node at (#1 - 1, -.8) {L$(j,k)$};
    \node at (#1 +. 5, 2.9) {S$(min(j*k,g),1)$};
    \node at (#1 + 2, -.8) {S$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
    \node at (#1, 3.3) {};
    \draw [] (#1 + .5, 2.01) circle [radius=0.4] node {$n$};
    \draw [] (#1 - 1, 0) circle [radius=0.4] node {$m$};
    \draw [] (#1 + 2, 0) circle [radius=0.4] node {$o$};
    \draw [->] (#1 - 1, .4) -- (#1 + .5, 2 - .4);
    \draw [<-] (#1 + 2, .4) -- (#1 + .5, 2 - .4);
}

@@

The rule \infrule{I-bisec} can be thought of as a programmer assertion about the bisection between two roles. The rule applies to an edge that has been annotated with a $bisec(X)$ statement, which means that there are $X$ disjoint paths between any node in role $m$ and any node in role $n$. Annotations of this form are useful for a "one big switch" \ryan{cite} type of abstraction where part of a complex network is abstracted into a single node.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figures/analysis}
  \end{center}
  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
  \label{fig:example-inference}
  \vspace{-1em}
\end{figure}

Consider again the datacenter example from \S\ref{sec:overview}. For global prefixes we used the routing policy:
%
\[ \begin{array}{c}
  \$PG \Path end(TG)
\end{array} \]
\noindent
%
Suppose now we additionally add the valleyfree constraint that traffic never has takes a path with a down-up in it. Figure~\ref{fig:example-inference} shows the abstract product graph representation for this routing policy. The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially). 
%
The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles. This invokes a call to Z3Opt to minimize the expression $min(\infty, AG)$, which gives us 2. Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
%
The next step uses the inference rule \infrule{I-out2} to learn that any single spine node is reachable. It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.

\ryan{inference should only infer some}

Note that, because each inference rule only applies to directed edges in the product graph, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them. It is this restriction that ensures that the analysis is both topology and policy dependent.

The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod P is reachable via at least 2 disjoint paths. This process will continue until a fixed point is reached.

In this case, the algorithm was able to infer that, with the valleyfree routing policy, any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a prefix originator in role TG. Note that, in this case, the analysis is precise. There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router. In this case, the analysis can be used to determine the number of failures that can induce an aggregation black-hole at the border of the datacenter.
